Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-19 paper/main.tex
Remove a few old comments to get a better sense what is done

\todo[inline]{SE: Clou der ganzen Geschichte ist doch: Man braucht keinen
separaten Localizer, oder? Das kommt bisher nur bedingt rüber; COH: well, if you
also want to have the ``visual part'' of the PPA then you need a visual
paradigm}

@@

\end{abstract}
\todo[inline]{RSC \& LOC are not mentioned in the abstract (anymore)}

\todo[inline]{our system cannot accept BibTeX bibliography files; authors who
    wish to use BibTeX to prepare their references should therefore copy the
    reference list from the .bbl file that BibTeX generates and paste it into
    the main manuscript .tex file (and delete the associated
    \textbackslash{}bibliography and \textbackslash{}bibliographystyle
commands)}

@@

\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.\todo{phrasing to delineate from Huth
(2016); imo voxel-wise semantic modeling says nothing about
excitation/inhibition}
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

@@

\todo[inline]{Specific data outputs should be explicitly referenced via data
citation (see Data Records and Data Citations, below)}

@@

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}.\todo{I guess they only report the ones they
designed themselves in detail? -> check again}
%
There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@

\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
Ausführungen, wie welche Annotation dazu passt; COH: revised but maybe still not
``optimal''}

>>>>

@@

\end{abstract}

@@

% Limit for main text (intro, results and discussion) = ca. 3k words

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.\todo{phrasing to delineate from Huth
(2016); imo voxel-wise semantic modeling says nothing about
excitation/inhibition}
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

@@

% Specific data outputs should be explicitly referenced via data
% citation (see Data Records and Data Citations, below)}

@@

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}.
%
There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@
